Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-11-22 doc/Paper/main.tex
Addressed comments from Masahiro.

  HSC-SSP is a photometric galaxy survey that has been awarded 300 nights on the Subaru Telescope starting in 2014. DR1 includes data from 61.5 nights observed to three different depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$). In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees. The image quality is impressive with a median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g. DES with around 0.9 arc sec) and also likely better than the median seeing expected to be achieved by LSST. The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.

  We use a magnitude-limited sample constructed from the WIDE DR1 sample by imposing data cuts that are similar to those used to create the HSC shear catalog \cite{2018PASJ...70S..25M}. The exact cuts are shown in Table~\ref{tab:cuts_summary}, and can be summarized as follows: besides a minimal set of quality cuts (selecting only primary detections with well-measured fluxes in all bands, removing objects near bad pixels, deblender artifacts, etc.), we impose an overall apparent magnitude cut in the extinction-corrected band $i_{\rm corr}<24.5$. This choice was based on a study of the survey depth-completeness relation in order to select a homogeneous and complete sample of high-confidence ($>10\sigma$) detections (see Section \ref{ssec:methods.syst}). We also select only objects with significant detections ($>5\sigma$) in at least two of the 4 remaining bands ($g,\,r,\,z,\,y$), and remove all objects classified as stars by the data reduction pipeline, using the ``extendedness'' classifier as described in \cite{2018PASJ...70S..25M,2018PASJ...70S...5B}. The resulting sample consists of 9,734,457 objects and covers $\sim88$ square degrees distributed across the 6 HSC DR1 fields, as described in Table \ref{tab:field_summary}. The $i$-band magnitude cut is by far the most stringent one, discarding approximately half of the total sample.

@@

    As noted above, the power spectra are computed in rings of $\ell=|{\bf l}|$, which we will call bandpowers here. We use 17 contiguous bandpowers with edges $\ell=$(100, 200, 300, 400, 600, 800, 1000, 1400, 1800, 2200, 3000, 3800, 4600, 6200, 7800, 9400, 12600, 15800). Due to this bandpower averaging, the estimated power spectra cannot, strictly speaking, be compared with theoretical predictions estimated at token multipoles (e.g. the midpoint of each band). The effect of this averaging can however be taken into account exactly as a linear operation of the form $\bar{C}_b=\sum_\ell F^b_{\ell} C_\ell$, where $C_\ell$ is the theoretical prediction evaluated at all integer multipoles $\ell$, $\bar{C}_b$ is the prediction for the $b$-th bandpower and the bandpower windows $F^b_{\ell}$ incorporate the effects of mode-coupling, averaging into bandpowers and the inversion of the binned mode-coupling matrix.

@@

  \subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
    Uncertainties in photometric redshifts (photo-$z$) represent one of the major systematics in photometric galaxy clustering analyses. To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies. In this work, we therefore choose to parametrize the impact of photo-$z$ errors on the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by
    \begin{equation}
      p_{i}(z) = \hat{p}_{i}(z_{c} + (1 + z_{w, i})(z-z_{c}) + \Delta z_{i}),
      \label{eq:photo-z-model}
    \end{equation} 
    where the index $i$ runs over the number of redshift bins considered in our analysis. In the above equation, $\hat{p}(z)$ denotes the estimated redshift distribution while $p(z)$ is the underlying true distribution. The parameters $\Delta z_{i}$ account for shifts in the means of the distributions and changes to their widths are parameterized through $z_{w, i}$. The quantity $z_{c}$ is kept constant in our analysis and is set to the redshift at which $\hat{p}(z)$ attains its maximal value.

@@

@@

      The positive side of the enhanced sensitivity of galaxy clustering to photometric redshift uncertainties compared to cosmic shear is the possibility of using clustering measurements to self-calibrate some of these uncertainties. As an example, our analysis hints towards a consistently positive value of the relative shift parameters $\Delta z_i-\Delta z_j,\,i>j$ (see e.g. Figs. \ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e.: the different bins are more widely separated than their fiducial distributions assumes. Since the signal-to-noise ratio of cosmic shear measurements tends to increase towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions). Although the data analysed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
          \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
          \label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
        \end{center}
      \end{figure}

>>>>

  HSC-SSP is a photometric galaxy survey that has been awarded 300 nights on the Subaru Telescope starting in 2014. DR1 includes data from 61.5 nights observed to three different depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$). In this work we focus on the HSC Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees. The image quality is impressive with a median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g. DES with around 0.9 arcsec) and also likely better than the median seeing expected to be achieved by LSST. The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.

  We use a magnitude-limited sample constructed from the HSC Wide DR1 sample by imposing data cuts that are similar to those used to create the HSC shear catalog \cite{2018PASJ...70S..25M}. The exact cuts are shown in Table~\ref{tab:cuts_summary}, and can be summarized as follows: besides a minimal set of quality cuts (selecting only primary detections with well-measured fluxes in all bands, removing objects near bad pixels, deblender artifacts, etc.), we impose an overall apparent magnitude cut in the extinction-corrected band $i_{\rm corr}<24.5$. This choice was based on a study of the survey depth-completeness relation in order to select a homogeneous and complete sample of high-confidence ($>10\sigma$) detections (see Section \ref{ssec:methods.syst}). We also select only objects with significant detections ($>5\sigma$) in at least two of the 4 remaining bands ($g,\,r,\,z,\,y$), and remove all objects classified as stars by the data reduction pipeline, using the ``extendedness'' classifier as described in \cite{2018PASJ...70S..25M,2018PASJ...70S...5B}. The resulting sample consists of 9,734,457 objects and covers $\sim88$ square degrees distributed across the 6 HSC DR1 fields, as described in Table \ref{tab:field_summary}. The $i$-band magnitude cut is by far the most stringent one, discarding approximately half of the total sample.

@@

    As noted above, the power spectra are computed in rings of $\ell=|{\bf l}|$, which we will call bandpowers here. We use 17 piecewise-linear, contiguous bandpowers with edges $\ell=$(100, 200, 300, 400, 600, 800, 1000, 1400, 1800, 2200, 3000, 3800, 4600, 6200, 7800, 9400, 12600, 15800)\footnote{This choice is motivated by mimicking logarithmic binning as closely as possible, while avoiding very small bin widths at low angular multipoles, which typically arise for logarithmic binning schemes.}. Due to this bandpower averaging, the estimated power spectra cannot, strictly speaking, be compared with theoretical predictions estimated at token multipoles (e.g. the midpoint of each band). The effect of this averaging can however be taken into account exactly as a linear operation of the form $\bar{C}_b=\sum_\ell F^b_{\ell} C_\ell$, where $C_\ell$ is the theoretical prediction evaluated at all integer multipoles $\ell$, $\bar{C}_b$ is the prediction for the $b$-th bandpower and the bandpower windows $F^b_{\ell}$ incorporate the effects of mode-coupling, averaging into bandpowers and the inversion of the binned mode-coupling matrix.

@@

  \subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
    Uncertainties in photometric redshifts (photo-$z$) represent one of the major systematics in photometric galaxy clustering analyses. To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies. In this work, we therefore choose to parametrize the impact of photo-$z$ errors on the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by
    \begin{equation}
      p_{i}(z) \propto \hat{p}_{i}(z_{c} + (1 + z_{w, i})(z-z_{c}) + \Delta z_{i}),
      \label{eq:photo-z-model}
    \end{equation} 
    where the index $i$ runs over the number of redshift bins considered in our analysis. In the above equation, $\hat{p}_{i}(z)$ denotes the estimated redshift distribution while $p_{i}(z)$ is the underlying true distribution. The parameters $\Delta z_{i}$ account for shifts in the means of the distributions and changes to their widths are parameterized through $z_{w, i}$. The quantity $z_{c}$ is kept constant in our analysis and is set to the redshift at which $\hat{p}_{i}(z)$ attains its maximal value. The normalization of the redshift distribution $p_{i}(z)$ depends on both $\Delta z_{i}$ and $z_{w, i}$ and we do not account for it in Eq.~\ref{eq:photo-z-model} for clarity.

@@

Finally we note that using the galaxy number density $\bar{n}$ as an additional data point in Eq.~\ref{eq:likelihood} has the potential to improve the constraining power of the data on HOD parameters, as it effectively fixes one of the parameters (see e.g. \cite{Zhai:2017}). However, we have chosen to not include this additional constraint in our analysis, as including it would require the modeling of the effects of photometric redshift errors and observational systematics on the estimated number density $\hat{\bar{n}}$, which is beyond the scope of this paper.

@@

      The positive side of the enhanced sensitivity of galaxy clustering to photometric redshift uncertainties compared to cosmic shear is the possibility of using clustering measurements to self-calibrate some of these uncertainties. As an example, our analysis hints towards a consistently positive value of the relative shift parameters $\Delta z_i-\Delta z_j,\,i>j$ (see e.g. Figs. \ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e. the different bins are more widely separated than their fiducial distributions assume. Since the signal-to-noise ratio of cosmic shear measurements tends to increase towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions). Although the data analysed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
          \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
          \label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
        \end{center}
      \end{figure}
